Why Donors Donate?

### 2020-09-11 analysis/05_market_simulator.Rmd

# Beta's of everything. The only model we care about right now
public_political_social_charity_demo <- readRDS(here('analysis', 'output', 'posterior_draws', 'public_political_social_charity_demo.rds')) %>% 
  group_by(i, j) %>% 
  summarize(gamma_mean = mean(Gamma)) %>% 
  ungroup() %>% 
  pivot_wider(names_from = j, values_from = gamma_mean) %>% 
  select(-i) %>% 
  t()

# Persona Data from Market Simulator Workbook
persona_data <- readxl::read_xlsx(here('analysis', 'output', "persona_configV06.xlsx"))

@@

beta$levels = c("Amnesty International",
                "Greenpeace", 
                "Oxfam", 
                "Red Cross",
                # Org Issue
                "Environment", 
                "Human rights",
                "Refugee relief",
                # Transparency
                "Engages in transparency",
                # Financial Accountability
                "Engages in financial accountability",
                # Funding
                "Handful of wealthy private donors", 
                "Government grants",
                # Gov Relations
                "Criticized by government",
                "Under government crackdown")

@@

beta_persona <- as.data.frame(matrix(rep(0), nrow = 111))

@@

@@

                        "Online (not social media)",
                        "Social media",

@@

                        "Email newsletter",

@@

                        "Often", 
                        # Travel to developing Countries
                        "Yes", 

@@

                        "Somewhat liberal",
                        "Slightly liberal",
                        "Moderate",
                        "Slightly conservative",
                        "Somewhat conservative",
                        "Extremely conservative",

@@

                        "Very little trust",
                        "Little trust",
                        "Nuetral",
                        "Some trust",
                        "A lot of trust",
                        "Complete trust",

@@

                        "Disagree",
                        "Somewhat disagree",
                        "Nuetral",
                        "Somewhat agree",
                        "Agree",
                        "Strongly agree",
                        # Worship Service Attendance
                        "At least once a month",

@@

                        "Important",

@@

                        "Very unimportant",
                        "Somewhat unimportant",
                        "Nuetral",
                        "Somewhat important",
                        "Very important",
                        "Essential",

@@

                        "Very little trust",
                        "Little trust",
                        "Nuetral",
                        "Some trust",
                        "A lot of trust",
                        "Complete trust",

@@

                        "At least once a month", 

@@

                        "$50-$99",
                        "$100-$499",
                        "$500-$999",
                        "$1,000-$4,999",
                        "$5,000-$9,999",
                        "$10,000 +",

@@

                        "Yes",

@@

                        "More than once a month, less than once a year",
                        "At least once a month",

@@

                        "Involved",

@@

                        "Involved",
                        # Religious Membership
                        "Inactive member",
                        "Active member",

@@

                        "Inactive member",
                        "Active member", 

@@

                        "Inactive member",
                        "Active member",

@@

                        "Inactive member",
                        "Active member",

@@

                        "Inactive member",
                        "Active member",

@@

                        "Inactive member",
                        "Active member",

@@

                        "Inactive member",
                        "Active member",

@@

                        "Inactive member",
                        "Active member",

@@

                        "Inactive member",
                        "Active member",

@@

                        "Inactive member",
                        "Active member",

@@

                        "Never married",

@@

                        "High school graduate", 
                        "Some college",
                        "2 year degree",
                        "4 year degree",
                        "Graduate or professional degree",
                        "Doctorate",

@@

                        "More than median of $61,372", 

@@

                        "Black or African American", 
                        "American Indian or Alaska Native", 

@@

                        "Native Hawaiian or Pacific Islander", 

@@

                        "More than median age of 36")

@@

@@

@@

selectInput("p1_national_news",
         label = "Follow national news:",
         choices = c("Rarely",
                     "Once a week",
                     "At least once a day"))

selectInput("p1_international_news",
         label = "Follow international news:",
         choices = c("Never",
                     "Sometimes",
                     "Always"))

selectInput("p1_news_medium",
         label = "Medium to follow news:",
         choices = c("TV",
                     "Print",
                     "Online (not social media)",
                     "Social media",
                     "Radio",
                     "Email newsletter",
                     "News app"),
         multiple = TRUE)

selectInput("p1_follow_gov",
         label = "Follow government & public affairs:",
         choices = c("Not Often",
                     "Often"))

selectInput("p1_travel_developing",
         label = "Travel to developing country:",
         choices = c('No', "Yes"))

selectInput("p1_political_pref",
         label = "Political views from liberal to conservative:",
         choices = c("Extremely liberal",
                     "Somewhat liberal",
                     "Slightly liberal",
                     "Moderate",
                     "Slightly conservative",
                     "Somewhat conservative",
                     "Extremely conservative"))

selectInput("p1_institution_trust",
         label = "Political institution trust from none to complete:",
         choices = c("No trust at all",
                     "Very little trust",
                     "Little trust",
                     "Nuetral",
                     "Some trust",
                     "A lot of trust",
                     "Complete trust"))

selectInput("p1_others_charitable",
         label = "People should be more charitable:",
         choices = c("Strongly Disagree",
                     "Disagree",
                     "Somewhat disagree",
                     "Nuetral",
                     "Somewhat agree",
                     "Agree",
                     "Strongly agree"))

selectInput("p1_worship_attendance",
         label = "Worship service attendance:",
         choices = c("Not sure",
                     "Rarely",
                     "At least once a month"))

selectInput("p1_religion_importance",
         label = "Importance of religion:",
         choices = c("Not important",
                     "Important"))

@@

selectInput("p1_charity_importance",
          label = "Charity Importance:",
          choices = c("Not at all important",
                      "Very unimportant",
                      "Somewhat unimportant",
                      "Nuetral",
                      "Somewhat important",
                      "Very important",
                      "Essential"))

selectInput("p1_trust_in_charity",
            label = "Charity Trust:",
            choices = c("No trust at all",
                        "Very little trust",
                        "Little trust",
                        "Nuetral",
                        "Some trust",
                        "A lot of trust",
                        "Complete trust"))

selectInput("p1_donation_frequency",
         label = "Donation Frequency:",
         choices = c('More than once a month, less than once a year',
                     'At least once a month'))

selectInput("p1_donation_amount",
         label = "Donation Amount:",
         choices = c("$1-$49",
                     '$50-$99',
                     '$100-$499',
                     '$500-$999',
                     '$1,000-$4,999',
                     '$5,000-$9,999',
                     '$10,000+'))

selectInput("p1_volunteer_12",
         label = "Volunteered in last 12 Months:",
         choices = c("No", "Yes"))

selectInput("p1_volunteer_frequency",
         label = "Volunteer Frequency:",
         choices = c("Haven't volunteered in past 12 months",
                     "Rarely",
                     "More than once a month, less than once a year",
                     "At least once a month"))

selectInput("p1_personal_activism",
         label = "Personal Activism:",
         choices = c('Not involved',
                     'Involved'))

selectInput("p1_family_activism",
         label = "Family Activism:",
         choices = c('Not involved',
                     'Involved'))

selectInput("p1_religious_member",
         label = "Church Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p1_sport_member",
         label = "Sport or Recreational Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p1_art_member",
         label = "Art, Music, or Educational Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p1_labor_member",
         label = "Labor Union Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p1_political_member",
         label = "Political Party Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p1_environmental_member",
         label = "Enviornmental Org. Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p1_professional_member",
         label = "Professional Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p1_humanitarian_member",
         label = "Humanitarian Org. Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p1_consumer_member",
         label = "Consumer Org. Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p1_other_member",
         label = "Other Org. Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

@@

selectInput("p1_education",
         label = "Education:",
         choices = c("Less than high school",
                     "High school graduate",
                     "Some college",
                     "2 year degree",
                     "4 year degree",
                     "Graduate or professional degree",
                     "Doctorate"))

selectInput("p1_income",
         label = "Income:",
         choices = c('Less than median of $61,372',
                     'More than median of $61,372'))

@@

selectInput("p1_age",
         label = "Age:",
         choices = c('Less than median age of 36',
                     "More than median age of 36"))

@@

selectInput("p2_national_news",
         label = "Follow national news:",
         choices = c("Rarely",
                     "Once a week",
                     "At least once a day"))

selectInput("p2_international_news",
         label = "Follow international news:",
         choices = c("Never",
                     "Sometimes",
                     'Always'))

selectInput("p2_news_medium",
         label = "Medium to follow news:",
         choices = c('TV',
                     'Print',
                     "Online (not social media)",
                     "Social media",
                     "Radio",
                     "Email newsletter",
                     "News app"),
         multiple = TRUE)

selectInput("p2_follow_gov",
         label = "Follow government & public affairs:",
         choices = c("Not Often",
                     "Often"))

selectInput("p2_travel_developing",
         label = "Travel to developing country:",
         choices = c('No', "Yes"))

selectInput("p2_political_pref",
         label = "Political views from liberal to conservative:",
         choices = c("Extremely liberal",
                     "Somewhat liberal",
                     "Slightly liberal",
                     "Moderate",
                     "Slightly conservative",
                     "Somewhat conservative",
                     "Extremely conservative"))

selectInput("p2_institution_trust",
         label = "Political institution trust from none to complete:",
         choices = c("No trust at all",
                     "Very little trust",
                     "Little trust",
                     "Nuetral",
                     "Some trust",
                     "A lot of trust",
                     "Complete trust"))

selectInput("p2_others_charitable",
         label = "People should be more charitable:",
         choices = c("Strongly Disagree",
                     "Disagree",
                     "Somewhat disagree",
                     "Nuetral",
                     "Somewhat agree",
                     "Agree",
                     "Strongly agree"))

selectInput("p2_worship_attendance",
         label = "Worship service attendance:",
         choices = c("Not sure",
                     "Rarely",
                     "At least once a month"))

selectInput("p2_religion_importance",
         label = "Importance of religion:",
         choices = c("Not important",
                     "Important"))

@@

selectInput("p2_charity_importance",
          label = "Charity Importance:",
          choices = c("Not at all important",
                      "Very unimportant",
                      "Somewhat unimportant",
                      "Nuetral",
                      "Somewhat important",
                      "Very important",
                      "Essential"))

selectInput("p2_trust_in_charity",
            label = "Charity Trust:",
            choices = c("No trust at all",
                        "Very little trust",
                        "Little trust",
                        "Nuetral",
                        "Some trust",
                        "A lot of trust",
                        "Complete trust"))

selectInput("p2_donation_frequency",
         label = "Donation Frequency:",
         choices = c('More than once a month, less than once a year',
                     'At least once a month'))

selectInput("p2_donation_amount",
         label = "Donation Amount:",
         choices = c("$1-$49",
                     '$50-$99',
                     '$100-$499',
                     '$500-$999',
                     '$1,000-$4,999',
                     '$5,000-$9,999',
                     '$10,000+'))

selectInput("p2_volunteer_12",
         label = "Volunteered in last 12 Months:",
         choices = c("No", "Yes"))

selectInput("p2_volunteer_frequency",
         label = "Volunteer Frequency:",
         choices = c("Haven't volunteered in past 12 months",
                     "Rarely",
                     "More than once a month, less than once a year",
                     "At least once a month"))

selectInput("p2_personal_activism",
         label = "Personal Activism:",
         choices = c('Not involved',
                     'Involved'))

selectInput("p2_family_activism",
         label = "Family Activism:",
         choices = c('Not involved',
                     'Involved'))

selectInput("p2_religious_member",
         label = "Church Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p2_sport_member",
         label = "Sport or Recreational Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p2_art_member",
         label = "Art, Music, or Educational Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p2_labor_member",
         label = "Labor Union Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p2_political_member",
         label = "Political Party Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p2_environmental_member",
         label = "Enviornmental Org. Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p2_professional_member",
         label = "Professional Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p2_humanitarian_member",
         label = "Humanitarian Org. Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p2_consumer_member",
         label = "Consumer Org. Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

selectInput("p2_other_member",
         label = "Other Org. Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

@@

selectInput("p2_education",
         label = "Education:",
         choices = c("Less than high school",
                     "High school graduate",
                     "Some college",
                     "2 year degree",
                     "4 year degree",
                     "Graduate or professional degree",
                     "Doctorate"))

selectInput("p2_income",
         label = "Income:",
         choices = c('Less than median of $61,372',
                     'More than median of $61,372'))

selectInput("p2_race",
         label = "Race(s):",
         choices = c('White',
                     'Black or African American',
                     'American Indian or Alaska Native',
                     'Asian',
                     'Native Hawaiian or Pacific Islander',
                     'Other (Race)'),
         multiple = TRUE)

selectInput("p2_age",
         label = "Age:",
         choices = c('Less than median age of 36',
                     "More than median age of 36"))

@@

selectInput("p3_national_news",
         label = "Follow national news:",
         choices = c("Rarely",
                     "Once a week",
                     "At least once a day"))

selectInput("p3_international_news",
         label = "Follow international news:",
         choices = c("Never",
                     "Sometimes",
                     'Always'))

selectInput("p3_news_medium",
         label = "Medium to follow news:",
         choices = c('TV',
                     'Print',
                     "Online (not social media)",
                     "Social media",
                     "Radio",
                     "Email newsletter",
                     "News app"),
         multiple = TRUE)

selectInput("p3_follow_gov",
         label = "Follow government & public affairs:",
         choices = c("Not Often",
                     "Often"))

selectInput("p3_travel_developing",
         label = "Travel to developing country:",
         choices = c('No', "Yes"))

selectInput("p3_political_pref",
         label = "Political views from liberal to conservative:",
         choices = c("Extremely liberal",
                     "Somewhat liberal",
                     "Slightly liberal",
                     "Moderate",
                     "Slightly conservative",
                     "Somewhat conservative",
                     "Extremely conservative"))

selectInput("p3_institution_trust",
         label = "Political institution trust from none to complete:",
         choices = c("No trust at all",
                     "Very little trust",
                     "Little trust",
                     "Nuetral",
                     "Some trust",
                     "A lot of trust",
                     "Complete trust"))

selectInput("p3_others_charitable",
         label = "People should be more charitable:",
         choices = c("Strongly Disagree",
                     "Disagree",
                     "Somewhat disagree",
                     "Nuetral",
                     "Somewhat agree",
                     "Agree",
                     "Strongly agree"))

selectInput("p3_worship_attendance",
         label = "Worship service attendance:",
         choices = c("Not sure",
                     "Rarely",
                     "At least once a month"))

selectInput("p3_religion_importance",
         label = "Importance of religion:",
         choices = c("Not important",
                     "Important"))

@@

selectInput("p3_charity_importance",
          label = "Charity Importance:",
          choices = c("Not at all important",
                      "Very unimportant",
                      "Somewhat unimportant",
                      "Nuetral",
                      "Somewhat important",
                      "Very important",
                      "Essential"))

>>>>

# Beta's of everything. The only model we care about right now
public_political_social_charity_demo <- readRDS(here('analysis', 'output', 'posterior_draws', 'public_political_social_charity_demo.rds')) %>% 
  group_by(i, j) %>% 
  summarize(gamma_mean = mean(Gamma)) %>% 
  ungroup() %>% 
  pivot_wider(names_from = j, values_from = gamma_mean) %>% 
  select(-i)

# Persona Data from Market Simulator Workbook
persona_data <- readxl::read_xlsx(here('analysis', 'output', "persona_config.xlsx"))

@@

beta$levels = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross", "Environment", "Human rights", "Refugee relief", "Engages in transparency", "Engages in financial accountability","Handful of wealthy private donors", "Government Grants", "Criticized by government", "Under government crackdown")

@@

beta_persona <- as.data.frame(matrix(rep(0), nrow = 61))

@@

                        "Never",

@@

                        "Online (excluding social media)",
                        "Social Media",

@@

                        "Email",

@@

                        "", 
                        # Travel to Countries
                        "Doesn't Travel", 

@@

                        "Political Preference", 

@@

                        "Trust in Political Institutions",

@@

                        "Others Should be Charitable",
                        # Worship Service Attendence
                        "Worship Service Attendence",

@@

                        "Religious Importance",

@@

                        "Chartiy Trust Importance",

@@

                        "Trust in Charity", 

@@

                        "Donation Frequency", 

@@

                        "Donation Amount",

@@

                        "Not Volunteered",

@@

                        "Volunteer Frequency",

@@

                        "Personal Activism",

@@

                        "Family Activism",
                        # Relgious Membership
                        "Religious Membership", 

@@

                        "Sport or Recreational Membership", 

@@

                        "Art, Music, or Educational Membership",

@@

                        "Labor Union Membership",

@@

                        "Political Party Membership",

@@

                        "Environmental Organization Membership",

@@

                        "Professional Association", 

@@

                        "Humanitarian or Charity Membership",

@@

                        "Consumer Organization Membership",

@@

                        "Other Organization Membership",

@@

                        "Never Married",

@@

                        "Education", 

@@

                        "Income", 

@@

                        "Black", 
                        "American Indian", 

@@

                        "Pacific Islander", 

@@

                        "Age")

@@

p1_politic_pref <- reactive({
  max(input$p1_political_pref)
})

@@

# beta_test <- as.data.frame(matrix(rep(0), nrow = 13))
# 
# beta_test$levels = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross", "Environment", "Human rights", "Refugee relief", "Engages in transparency", "Engages in financial accountability","Handful of wealthy private donors", "Government Grants", "Criticized by government", "Under government crackdown")
# 
# beta_test$ai_issue <- 0
# beta_test$ai_issue[4] <- 1
# beta_test$ai_issue[8] <- 1
# beta_test$ai_issue[9] <- 1
# 
# 
# beta_test$gp_issue <- 0
# beta_test$gp_issue[4] <- 1
# beta_test$gp_issue[5] <- 1
# beta_test$gp_issue[8] <- 1
# beta_test$gp_issue[9] <- 1
# 
# 
# beta_test$ox_issue <- 0
# beta_test$ox_issue[4] <- 1
# beta_test$ox_issue[6] <- 1
# beta_test$ox_issue[8] <- 1
# beta_test$ox_issue[9] <- 1
# 
# beta_test$rc_issue <- 0
# beta_test$rc_issue[4] <- 1
# beta_test$rc_issue[7] <- 1
# beta_test$rc_issue[8] <- 1
# beta_test$rc_issue[9] <- 1
# 
# 
# 
#   ai_exp_util1 <- round(exp(t(beta_test[, 3]) %*% as.matrix(p_beta1)),2)
#   gp_exp_util1 <- round(exp(t(beta_test[, 4]) %*% as.matrix(p_beta1)),2)
#   ox_exp_util1 <- round(exp(t(beta_test[, 5]) %*% as.matrix(p_beta1)),2)
#   rc_exp_util1 <- round(exp(t(beta_test[, 6]) %*% as.matrix(p_beta1)),2)
# 
#   ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
#   gp_rate1 <- round(100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
#   ox_rate1 <- round(100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
#   rc_rate1 <- round(100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))

@@

# Need to Fix
selectInput("p1_national_news",
         label = "Follow national news:",
         choices = c("Atleast once a day",
                     "Once a week",
                     "Rarely"
                     ))

# Need to Fix
selectInput("p1_international_news",
         label = "Follow international news:",
         choices = c('Always',
                     "Sometimes",
                     "Never"))

selectInput("p1_news_medium",
         label = "Medium to follow news:",
         choices = c('TV',
                     'Print',
                     "Online (excluding social media)",
                     "Social Media",
                     "Radio",
                     "Email",
                     "News app"),
         multiple = TRUE)

# Need to Fix
selectInput("p1_follow_gov",
         label = "Follow government & public affairs:",
         choices = c('Most of the time',
                     'Some of the time',
                     "Only now and then",
                     "Hardly at all"))

selectInput("p1_travel_developing",
         label = "Travel to developing country:",
         choices = c('Does Travel', "Doesn't Travel"))

# Need to Fix
selectInput("p1_political_pref",
         label = "Political views from liberal to conservative:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

# Need to Fix
selectInput("p1_institution_trust",
         label = "Political institution trust from none to complete:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

# Need to Fix
selectInput("p1_others_charitable",
         label = "People should be more charitable:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

# Need to Fix
selectInput("p1_worship_attendance",
         label = "Worship service attendance:",
         choices = c('Multiple times a week',
                     'Once a week',
                     "Once a month",
                     "Few times a year",
                     "Once a year",
                     "Never"))

# Need to Fix
selectInput("p1_religion_importance",
         label = "Importance of religion:",
         choices = c('Extremely important',
                     'Very important',
                     'Moderately important',
                     'Slightly important',
                     'Not at all important'))

@@

# Need to Fix
selectInput("p1_charity_importance",
          label = "Charity Importance:",
          choices = c("0", '1', '2', '3','4','5','6','7'))

# Need to Fix
selectInput("p1_trust_in_charity",
            label = "Charity Trust:",
            choices = c("0", '1', '2', '3','4','5','6','7'))

# Need to Fix

selectInput("p1_donation_frequency",
         label = "Donation Frequency:",
         choices = c('Once a week',
                     'Once a Month',
                     'Once every three months',
                     'Once every six months',
                     'Once a year',
                     'Once every few years',
                     'Never'))

# Need to Fix
selectInput("p1_donation_amount",
         label = "Donation Amount:",
         choices = c("$1-$49",
                     '$50-$99',
                     '$100-$499',
                     '$500-$999',
                     '$1,000-$4,999',
                     '$5,000-$9,999',
                     '$10,000+'))

selectInput("p1_volunteer_12",
         label = "Volunteered in last 12 Months:",
         choices = c("Volunteered", "Not Volunteered"))

# Need to Fix
selectInput("p1_volunteer_frequency",
         label = "Volunteer Frequency:",
         choices = c('Once a week',
                     'Once a Month',
                     'Once every three months',
                     'Once every six months',
                     'Once a year',
                     'Once every few years'))

# Need to Fix
selectInput("p1_personal_activism",
         label = "Personal Activism:",
         choices = c('Extremely involved',
                     'Very involved',
                     'Moderately involved',
                     'Slightly involved',
                     'Never involved'))

# Need to Fix
selectInput("p1_family_activism",
         label = "Family Activism:",
         choices = c('Extremely involved',
                     'Very involved',
                     'Moderately involved',
                     'Slightly involved',
                     'Never involved'))

# Need to Fix
selectInput("p1_religious_member",
         label = "Church Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p1_sport_member",
         label = "Sport or Recreational Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p1_art_member",
         label = "Art, Music, or Educational Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p1_labor_member",
         label = "Labor Union Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p1_political_member",
         label = "Political Party Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p1_environmental_member",
         label = "Enviornmental Org. Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p1_professional_member",
         label = "Professional Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p1_humanitarian_member",
         label = "Humanitarian Org. Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p1_consumer_member",
         label = "Consumer Org. Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p1_other_member",
         label = "Other Org. Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

@@

# Need to Fix
selectInput("p1_education",
         label = "Education:",
         choices = c("Less than high school",
                     "High school",
                     "Some college",
                     "2 year degree",
                     "4 year degree",
                     "Graduate degree",
                     "Doctorate"))
# Need to Fix
selectInput("p1_income",
         label = "Income:",
         choices = c('Less than $10,000',
                     '$10,000 to $19,999',
                     '$20,000 to $29,999',
                     '$30,000 to $39,999',
                     '$40,000 to $49,999',
                     '$50,000 to $59,999',
                     '$60,000 to $69,999',
                     '$70,000 to $79,999',
                     '$80,000 to $89,999',
                     '$90,000 to $99,999',
                     '$100,000 to $149,999',
                     '$150,000 to $199,999',
                     '$200,000 to $299,999',
                     '$300,000 or more'))

@@

# Need to Fix
selectInput("p1_age",
         label = "Age:",
         choices = c('Under 18',
                     '18 - 24',
                     '25 - 34',
                     '35 - 44',
                     '45 - 54',
                     '55 - 64',
                     '65 - 74',
                     '75 - 84',
                     '85 or older'))

@@

# Need to Fix
selectInput("p2_national_news",
         label = "Follow national news:",
         choices = c('Multiple times a day',
                     'Every day',
                     "Once a week",
                     "Hardly ever",
                     "Never"))

# Need to Fix
selectInput("p2_international_news",
         label = "Follow international news:",
         choices = c('Always',
                     "Sometimes",
                     "Never"))

selectInput("p2_news_medium",
         label = "Medium to follow news:",
         choices = c("",
                     'TV',
                     'Print',
                     "Online (excluding social media)",
                     "Social Media",
                     "Radio",
                     "Email",
                     "News app"),
         multiple = TRUE)

# Need to Fix
selectInput("p2_follow_gov",
         label = "Follow government & public affairs:",
         choices = c('Most of the time',
                     'Some of the time',
                     "Only now and then",
                     "Hardly at all"))

selectInput("p2_travel_developing",
         label = "Travel to developing country:",
         choices = c('Does Travel', "Doesn't Travel"))

# Need to Fix
selectInput("p2_political_pref",
         label = "Political views from liberal to conservative:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

# Need to Fix
selectInput("p2_institution_trust",
         label = "Political institution trust from none to complete:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

# Need to Fix
selectInput("p2_others_charitable",
         label = "People should be more charitable:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

# Need to Fix
selectInput("p2_worship_attendance",
         label = "Worship service attendance:",
         choices = c('Multiple times a week',
                     'Once a week',
                     "Once a month",
                     "Once a year",
                     "Never"))

# Need to Fix
selectInput("p2_religion_importance",
         label = "Importance of religion:",
         choices = c('Extremely important',
                     'Very important',
                     'Moderately important',
                     'Slightly important',
                     'Not at all important'))

@@

# Need to Fix
selectInput("p2_charity_importance",
          label = "Charity Importance:",
          choices = c("0", '1', '2', '3','4','5','6','7'))

# Need to Fix
selectInput("p2_trust_in_charity",
            label = "Charity Trust:",
            choices = c("0", '1', '2', '3','4','5','6','7'))

# Need to Fix

selectInput("p2_donation_frequency",
         label = "Donation Frequency:",
         choices = c('Once a week',
                     'Once a Month',
                     'Once every three months',
                     'Once every six months',
                     'Once a year',
                     'Once every few years',
                     'Never'))

# Need to Fix
selectInput("p2_donation_amount",
         label = "Donation Amount:",
         choices = c("$1-$49",
                     '$50-$99',
                     '$100-$499',
                     '$500-$999',
                     '$1,000-$4,999',
                     '$5,000-$9,999',
                     '$10,000+'))

selectInput("p2_volunteer_12",
         label = "Volunteered in last 12 Months:",
         choices = c("Volunteered", "Not Volunteered"))

# Need to Fix
selectInput("p2_volunteer_frequency",
         label = "Volunteer Frequency:",
         choices = c('Once a week',
                     'Once a Month',
                     'Once every three months',
                     'Once every six months',
                     'Once a year',
                     'Once every few years',
                     'Never'))

# Need to Fix
selectInput("p2_personal_activism",
         label = "Personal Activism:",
         choices = c('Extremely involved',
                     'Very involved',
                     'Moderately involved',
                     'Slightly involved',
                     'Never involved'))

# Need to Fix
selectInput("p2_family_activism",
         label = "Family Activism:",
         choices = c('Extremely involved',
                     'Very involved',
                     'Moderately involved',
                     'Slightly involved',
                     'Never involved'))

# Need to Fix
selectInput("p2_religious_member",
         label = "Church Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p2_sport_member",
         label = "Sport or Recreational Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p2_art_member",
         label = "Art, Music, or Educational Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p2_labor_member",
         label = "Labor Union Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p2_political_member",
         label = "Political Party Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p2_environmental_member",
         label = "Enviornmental Org. Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p2_professional_member",
         label = "Professional Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p2_humanitarian_member",
         label = "Humanitarian Org. Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p2_consumer_member",
         label = "Consumer Org. Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p2_other_member",
         label = "Other Org. Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

@@

# Need to Fix
selectInput("p2_education",
         label = "Education:",
         choices = c("Less than high school",
                     "High school",
                     "Some college",
                     "2 year degree",
                     "4 year degree",
                     "Graduate degree",
                     "Doctorate"))
# Need to Fix
selectInput("p2_income",
         label = "Income:",
         choices = c('Less than $10,000',
                     '$10,000 to $19,999',
                     '$20,000 to $29,999',
                     '$30,000 to $39,999',
                     '$40,000 to $49,999',
                     '$50,000 to $59,999',
                     '$60,000 to $69,999',
                     '$70,000 to $79,999',
                     '$80,000 to $89,999',
                     '$90,000 to $99,999',
                     '$100,000 to $149,999',
                     '$150,000 to $199,999',
                     '$200,000 to $299,999',
                     '$300,000 or more'))

selectInput("p2_race",
         label = "Race(s):",
         choices = c("",
                     'White',
                     'Black or African American',
                     'American Indian or Alaska Native',
                     'Asian',
                     'Native Hawaiian or Pacific Islander',
                     'Other (Race)'),
         multiple = TRUE)

# Need to Fix
selectInput("p2_age",
         label = "Age:",
         choices = c('Under 18',
                     '18 - 24',
                     '25 - 34',
                     '35 - 44',
                     '45 - 54',
                     '55 - 64',
                     '65 - 74',
                     '75 - 84',
                     '85 or older'))

@@

# Need to Fix
selectInput("p3_national_news",
         label = "Follow national news:",
         choices = c('Multiple times a day',
                     'Every day',
                     "Once a week",
                     "Hardly ever",
                     "Never"))

# Need to Fix
selectInput("p3_international_news",
         label = "Follow international news:",
         choices = c('Always',
                     "Sometimes",
                     "Never"))

selectInput("p3_news_medium",
         label = "Medium to follow news:",
         choices = c("",
                     'TV',
                     'Print',
                     "Online (excluding social media)",
                     "Social Media",
                     "Radio",
                     "Email",
                     "News app"),
         multiple = TRUE)

# Need to Fix
selectInput("p3_follow_gov",
         label = "Follow government & public affairs:",
         choices = c('Most of the time',
                     'Some of the time',
                     "Only now and then",
                     "Hardly at all"))

selectInput("p3_travel_developing",
         label = "Travel to developing country:",
         choices = c('Does Travel', "Doesn't Travel"))

# Need to Fix
selectInput("p3_political_pref",
         label = "Political views from liberal to conservative:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

# Need to Fix
selectInput("p3_institution_trust",
         label = "Political institution trust from none to complete:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

# Need to Fix
selectInput("p3_others_charitable",
         label = "People should be more charitable:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

# Need to Fix
selectInput("p3_worship_attendance",
         label = "Worship service attendance:",
         choices = c('Multiple times a week',
                     'Once a week',
                     "Once a month",
                     "Once a year",
                     "Never"))

# Need to Fix
selectInput("p3_religion_importance",
         label = "Importance of religion:",
         choices = c('Extremely important',
                     'Very important',
                     'Moderately important',
                     'Slightly important',
                     'Not at all important'))

@@

# Need to Fix
selectInput("p3_charity_importance",
          label = "Charity Importance:",
          choices = c("0", '1', '2', '3','4','5','6','7'))

# Need to Fix
selectInput("p3_trust_in_charity",
            label = "Charity Trust:",
            choices = c("0", '1', '2', '3','4','5','6','7'))

# Need to Fix
